---
title: "P8105_hw4_yn2295"
author: "Yanelli Nunez & Lizzy Gibson"
date: "10/24/2017"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loading packages}
library(tidyverse)
library(janitor)
library(ggridges)
```

## Read and Clean Pups Data

The code below cleans the pups dataset and converts it from wide to long format.

```{r clean_pups}
pups_data = read_csv("./FAS_pups.csv") %>%
  clean_names() %>%
  gather(key = developmental_landmark, value = day, pd_ears:pd_walk) 
```

## Pups Data Visualization

This plot shows the distribution of post-natal days for each developmental landmark.

```{r pups_plot}
pups_data %>% 
  mutate(developmental_landmark = forcats::fct_recode(developmental_landmark,
                                                      "Ears" = "pd_ears",
                                                      "Eyes" = "pd_eyes",
                                                      "Pivot" = "pd_pivot",
                                                      "Walk" = "pd_walk")) %>% 
  ggplot(aes(x = day)) + 
  geom_histogram(color = "black", fill = "black", bins = 25) +
  facet_grid(developmental_landmark ~ .) +
  labs(x = "Post-natal days", y = "Counts", title = "Post-natal days for developmental landmarks") +
  theme_bw()
```

These histograms show that the ears are the first thing to develop in the pups after birth, followed by the ability to pivot and to walk (which overlap quite a bit), and the eyes are usually the last thing to develop.